1---
title: "Representing Categorical Data - Favorite Classes"
format: html
---

```{r}
library(tidyverse)
library(googlesheets4)
library(janitor)
```

```{r}
url = "https://docs.google.com/spreadsheets/d/1JmVLUjtSwcuxApJXFFYu7sbre7s0pHjOfz2bmnwDMnQ/edit?usp=sharing"
df = read_sheet(url) |> 
  clean_names()
```
# 1. Make a barplot of `what_is_your_favorite_core_class`

```{r}
df |> 
  ggplot() +
  aes(
    x = what_is_your_favorite_core_class, 
    color = what_is_your_favorite_core_class,
    fill = what_is_your_favorite_core_class
  ) +
  geom_bar() + 
  scale_color_brewer(type = "qual", palette = 1) +
  scale_fill_brewer(type = "qual", palette = 1) +
  labs(
    title = "KAT Stats Favorite Core Classes",
    x = "Favorite Core Class",
    y = "Frequency",
    color = NULL,
    fill = NULL
  )
```

# 2. Make a barplot of `what_is_your_favorite_elective_class`

```{r}
df |> 
  ggplot() +
  aes(
    x = what_is_your_favorite_elective_class, 
    color = what_is_your_favorite_elective_class,
    fill = what_is_your_favorite_elective_class
  ) +
  geom_bar() + 
  scale_color_brewer(type = "qual", palette = 2) +
  scale_fill_brewer(type = "qual", palette = 2) +
  labs(
    title = "KAT Stats Favorite Elective Classes",
    x = "Favorite Core Class",
    y = "Frequency",
    color = NULL,
    fill = NULL
  )
```

# 3. Make a stacked barplot of `what_is_your_favorite_core_class` and `what_is_your_favorite_elective_class`

```{r}
df |> 
  ggplot() +
  aes(
    x = what_is_your_favorite_core_class, 
    color = what_is_your_favorite_elective_class,
    fill = what_is_your_favorite_elective_class
  ) +
  geom_bar() + 
  scale_color_brewer(type = "qual", palette = 2) +
  scale_fill_brewer(type = "qual", palette = 2) +
  labs(
    title = "KAT Stats Favorite Core Classes",
    x = "Favorite Core Class",
    y = "Frequency",
    color = NULL,
    fill = NULL
  )
```

# 4. Make a side by side barplot of `what_is_your_favorite_core_class` and `what_is_your_favorite_elective_class`
```{r}
df |> 
  ggplot() +
  aes(
    x = what_is_your_favorite_core_class, 
    color = what_is_your_favorite_elective_class,
    fill = what_is_your_favorite_elective_class
  ) +
  geom_bar(position = "dodge") + 
  scale_color_brewer(type = "qual", palette = 2) +
  scale_fill_brewer(type = "qual", palette = 2) +
  labs(
    title = "KAT Stats Favorite Core Classes",
    x = "Favorite Core Class",
    y = "Frequency",
    color = NULL,
    fill = NULL
  )
```

